\documentclass[a4paper]{recipe}
    \usepackage[T1]{fontenc}
    \usepackage{bookman}
    \usepackage{textcomp}

    \newcommand{\bsi}[2]{%
      \fontencoding{T1}\fontfamily{pbs}\fontseries{xl}\fontshape{n}%
      \fontsize{#1}{#2}\selectfont}

    \renewcommand{\instructhead}{\textbf{Directions}: }
    \renewcommand{\inghead}{\textbf{Ingredients}: }
    \renewcommand{\yieldhead}{\textbf{Yield}: 10 Bars}
    \renewcommand{\servingshead}{\textbf{Serving Size}: 1 Bar\ }
    \renewcommand{\carbshead}{\textbf{Carbs}: }
    \renewcommand{\lifehead}{\textbf{Shelf Life}: 5 Days\ }

    \renewcommand{\rechead}{\centering\bsi{24pt}{30pt}}

    \makeatletter
    \renewcommand*\l@subsubsection{\@dottedtocline{3}{3em}{0em}}
    \makeatother

    \setlength\parindent{0pt}
    \setlength\parskip{2ex plus 0.5ex}
    \pagenumbering{gobble}

    \begin{document}
    \recipe{Breakfast Bars}
    \ingred{
        \item Rolled Oats, 2 cups
        \item Quiona, 3/4 cup
        \item Bulgur Wheat, 1/4 cup
        \item Pumpkin or Sunflower Seeds, 1 1/4 cups
        \item Dried Cranberries, 1/2 cup
        \item Maple Syrup, 1/2 cup
        \item Sun Butter, 1/2 cup
        \item Table Salt, 1/4 tsp
        \item Coconut Oil, 1/4 cup
        \item Brown Sugar, 2 tbsp
        \item Vanilla Extract, 1 tsp
    }
    
    \instruct{
        \item Heat your oven to 350.
        \item Line a 9 x 13-inch baking dish so some of the paper goes over the edge.
        \item Heat a large skillet over a medium-low heat and add the oats, quinoa, and millet. Stir them all around until they start to smell toasted, about 3 minutes. 
        \item Combine the seedss and cranberries in a large bowl. Pour in the toasted oat mix and the salt and mix together.
        \item In a small saucepan, combine the maple syrup, peanut butter, oil, sugar, and vanilla and warm until everything is melted and then remove from the heat.
        \item Pour this all over the dry mix and stir until everything is coated. 
        \item Pour the mixture into the baking dish and press it down with a spoon to even it out and pack it.
        \item Cook in the oven until it looks toasted, 25 to 30 minutes. 
        \item Let it cool to room temperature in the pan tand then move to the fridge.hen throw it into the fridge. 
        \item When it’s completely cooled, cut into bars. They keep best in the fridge.
    }


    \yieldhead \\
    \servingshead \\
    \carbshead \\
    \lifehead


    \end{document}
